SIR Model With Testing Flows and Isolation

### 2021-01-15 codes/sir_macpan.Rnw
minor updates

<<Read Data from Mike's repo, echo=T>>=
library(readr)

@@

plot_pos_prov <- ggplot(df_covid,aes(x=Date,y=confirmed_positive,col=Province))+
                  geom_point()

@@

>>>>

<<Read Data from Mike's repo, echo=T>>=
library(McMasterPandemic)
library(readr)
library(dplyr)
library(ggplot2); theme_set(theme_bw())
library(directlabels)

@@

## BMB: the fit was using *cumulative* cases before, 
## Ali I used confirmed_positive before
plot_pos_prov <- ggplot(df_covid,aes(x=Date,y=newConfirmations,col=Province))+
  geom_point()

@@

# Assume we are just looking at Ontario's epidemic case:

startdate <- as.Date("2020-12-11")
enddate <- as.Date("2021-01-12")
## BMB: if we use the original, short time series
##   Error in stats::filter(i, kern, sides = 1) : 
##     'filter' is longer than time series

df_covid_on <- (df_covid 
                %>% filter(Province =="ON", Date >= startdate) # Ontario
                %>% mutate(value= round(newConfirmations), var= "report", date=Date)
                %>% select(date, value, var)
                %>% na.omit()
)
## BMB: check length, beginning
nrow(df_covid_on)
head(df_covid_on,1)

## beta0 (and E0) the only parameter we're going to optimize:
params <- read_params("ICU1.csv")
## adjust to ON pop size, approx starting value:
## about 1800 cases reported
## adjust ascertainment rate (fraction of cases reported) to 1/3
## (was 0.1, which was reasonable at beginning of epidemic)
## (will just rescale results)
## so 1800 cases -> prevalence of approx 3*1800
## initial conditions automatically spread E0 over the eigenvector
params <- update(params, N=15e6,E0=3*1800, c_prop=1/3)

## set up optimization parameters
opt_pars <- get_opt_pars(params, vars="report")

params1obs <- update(params, obs_disp=20)

## document: bounds for DE optimization???

plot(run_sim(
    params = params1obs,
    start_date=startdate,
    end_date=enddate),
    keep_states="report", log=TRUE)

## fit beta0 based on the report data:
fitted.mod <- calibrate(
  data = df_covid_on
  , start_date = startdate
  ## skip breaks that are present by default:
, time_args = list(break_dates = NULL)
  , base_params = params1obs
, opt_pars = opt_pars
 , debug_plot = TRUE # instructive plotting during optimization
)

## plot the resulting fit
plot(fitted.mod,data=df_covid_on)

## FIXME in macpan: check for correct structure in opt_pars
## check length of time series?
## FIXME: shouldn't need to specify time_args ...
